Multi-Agent Pathfinding with Matching using Increasing Cost Tree Search

### 2021-06-27 docs/paper.tex
Clarified ICTS-m root definition

	\subsection{ICTS-m}
	ICTS with Matching (ICTS-m) generalizes ICTS to optimally solve MAPFM instances. Few changes to ICTS were necessary to accommodate for matching in this increasing cost tree scheme. Specifically, the ICT root generation and the MDD generation as described in Subsection \ref{icts} had to be changed.
	\subsubsection{Root generation for matching}
	Given a team $t_i$ of size $k_i$, for any agent $a_j^i$ there are $k_i$ costs $c_j(1),c_j(2),\ldots,c_j(k_i)$ for shortest paths from $s_j^i$ to each goal $g_k^i$. Making no assumptions about what goals other agents in $t_i$ are assigned to, it could be that in the optimal solution $a_j^i$ is assigned to a goal $g_{m}^i$ with path cost $c^*_j = c_j(m)$ such that $c_j(m) = \min_{n\in\{1,\ldots,k_i\}} c_j(n)$. Therefore, to guarantee optimality, the minimal cost to any matching goal has to take the place of the shortest path cost from the original ICTS root. Intuitively, the sum of individual costs of this root is highly optimistic, particularly if the teams are large. This is because often, agents will not move to their closest matching goal in an optimal solution, even without considering conflicts (see \ref{pathology}).

>>>>

	\subsection{ICTS-m}
	ICTS with Matching (ICTS-m) generalizes ICTS to optimally solve MAPFM instances. Few changes to ICTS were necessary to accommodate for matching in this increasing cost tree scheme. Specifically, the ICT root generation and the MDD generation as described in Subsection \ref{icts} had to be changed.
	\subsubsection{Root generation for matching}
	Given a team $t_i$ of size $k_i$, for any agent $a_j^i$ there are $k_i$ costs $c_j(1),c_j(2),\ldots,c_j(k_i)$ for shortest paths from $s_j^i$ to each goal $g_k^i$. Making no assumptions about what goals other agents in $t_i$ are assigned to, it could be that in the optimal solution $a_j^i$ is assigned to a goal $g_{m}^i$ with path cost $c^*_j = c_j(m)$ such that $c_j(m) = \min_{n\in\{1,\ldots,k_i\}} c_j(n)$. Therefore, to guarantee optimality, the minimal shortest path cost to any matching goal has to take the place of the shortest path cost from the original ICTS root. Intuitively, the sum of individual costs of this root is highly optimistic, particularly if the teams are large. This is because often, agents will not move to their closest matching goal in an optimal solution, even without considering conflicts (see \ref{pathology}).
